SI_ExtraPlots

### 2021-04-03 writeup-paper/draft_apa_blinded_revised.Rmd
April revisions to .rmd

  Social information plays a key role in infants\' early linguistic and cognitive development. Yet infants locomotor abilities also develop continuously as they learn to sit, crawl, stand, and walk. How do these postural developments affect infants access to the social information relevant for early learning? To address this question, we first created a rich annotated dataset of naturalistic play sessions between infants and their caregivers with sets of novel and familiar toys (N=36, 8-16 month-olds), recording both egocentric and third-person video. We then developed an automated analysis method using a pose detection model to detect the faces and hands in the infant view. We found that infants\' posture and orientation to their caregiver changed dramatically across this age range and modulated infants access to social information; infants who were sitting or standing with their caregiver at a close distance tended to have the most faces and hands in their visual field. We applied this automated method to a second egocentric video dataset from a previous study, replicating and extending their findings on the influence of infants' posture on the social information in view. Together, these results establish the validity of a new method for detecting social information in egocentric videos and confirm that motoric developments play a significant role in shaping the social information that infants have access to. The combined use of head-mounted cameras and new computer vision techniques is a promising avenue for understanding how the statistics of infants\' visual and linguistic experience change over development.

keywords          : "Postural developments, headcam, social information, face detection, pose detection"
wordcount         : "7324"

@@

figsintext        : yes
figurelist        : yes
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

@@

```{r, libraries}
library(knitr)
knitr::opts_chunk$set(fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=FALSE, message = FALSE, sanitize = TRUE)
library(readr)
library(dplyr)
library(tidyr)
library(xtable)
library(lubridate)
library(langcog)
library(ggplot2)
library(ggthemes)
library(lme4)
library(gridExtra)
library(assertthat)
library(tidyverse)
library(viridis)
library(papaja)
library(png)
library(magick)
library(lmerTest)
```

@@

From their earliest months, infants are deeply engaged in learning from others. Even newborns tend to prefer to look at faces with direct vs. averted gaze [@farroni2002eye] and young infants follow overt gaze shifts [@gredeback2010development; @bruner1975]. And as infants reach their first birthday, they also tend to follow [@yu2013joint; @yu2017hand] and imitate the gestures of their caregivers (e.g., pointing). Infants' ability to process these social cues may provide strong scaffolding for early word learning. Longitudinal studies provide some evidence for this link: children’s level of joint engagement with their mother at 9-12 months predicts both their receptive and productive vocabularies [@carpenter1998] and 10 month-olds who follow an adult’s gaze (in an experimental context) have larger vocabularies at 18 months and throughout the second year of life [@brooks2005; @brooks2008]. While the relationship between hand-following and language development has been less well characterized, infants who follow their caregivers’ hands tend to be those who spend more time jointly attending to events with their caregivers [@yu2017hand].

Relatively little work, however, has quantified how often infants see and use these kinds of social cues in naturalistic learning environments. By using head-mounted cameras to record what infants see, researchers have begun to document the infant egocentric perspective [@yoshida2008] and to quantify the information -- social and otherwise -- available to infants as they learn. While head-mounted camera data do not provide explicit information on where infants are attending, some work suggests that infants orient their head towards what they are focusing on -- putting those people or objects in view [@yoshida2008]. Initial recordings using this technique during in-lab play sessions revealed a different view than many imagined: instead of being dominated by faces, the infant perspective contained close up views of primarily toys and hands [@yoshida2008; @franchak2011; @yu2017hand]. Subsequent research has revealed that the infant view undergoes dramatic changes as infants grow. Recordings from home environments suggest that the viewpoints of very young infants -- less than 4 months of age -- do indeed contain persistent and frequent views of faces [@fausey2016; @jayaraman2017faces] but that the infant view tends to contain more and more hands as infants grow older.

These changes in perspective are likely the downstream consequence of myriad factors, chief of which may be infants' evolving locomotive abilities: an infant's ability to sit, crawl, stand, or walk structures the way they interact with the things and people in their world. Infants' locomotive abilities can change rapidly: the physical body of an infant can lengthen up to 2cm in 24 hours [@lampl1993evidence], leading to changes in their abilities from one day to the next. These motoric developments can be thought of as gateways that open up entirely new phases of development [@iverson2010], causing a cascade of changes in an infant's ability to interact with their world and the people in it [@karasik2014]. Thus, infants’ changing locomotor abilities may shape the social cues that infants see and seek out, in turn impacting their cognitive and linguistic abilities.

However, understanding the nuanced relationship between the social information in the infant view and their motoric and linguistic development has remained challenging. For example, as children begin crawling [@adolph1998roles] -- or scooting or cruising [@patrick2012developmental] -- they are no longer constrained to the same spot that their caregivers last placed them in. Yet while crawlers can choose where to go and what they see to a much greater degree, they also appear to spend much of their time in a world populated by floors and knees; during spontaneous play, toddlers are more likely to look at the floor while crawling than while walking [@franchak2011], when they have full visual access to their environment and the people in it [@kretch2014].
Further, infants' experience with sitting predicts their success at 3D object completion tasks [@soska2010systems] as well as their receptive vocabulary [@libertus2016sit], suggesting the importance of focused play sessions for language development.

Others have posited that it is children’s ability to stand and walk that fundamentally changes their ability to access social information (e.g., facial expressions, gaze cues, pointing) relative to children who are still crawling and sitting [@walle2016infant], which in turn allow infants to learn words quicker and more efficiently [@walle2016infant]. Supporting this idea, walking vs. crawling infants tend to make different kinds of object-related bids for attention from their caregivers [@karasik2014], hear more action directed statements (e.g., “open it”) [@karasik2014], and have higher receptive and productive vocabularies [@walle2014]. However, not all evidence supports this view: parental report data suggest a weak relationship between walking and the onset of language [@moore2019point], and head-mounted eye-tracking data from one-year-olds highlights the role of infants’ in-the-moment posture -- and that of their caregivers’ -- in what infants’ see, finding that these factors are better predictors of the social information in view than their locomotor status per se (i.e., “walker” vs “crawler”) [@franchak2017see].

Broadly, the field is in need of computational tools to reuse these rich video datasets and understand the generalizability of findings across different populations, tasks, and age-ranges. For example, different kinds of play sessions (e.g., exploring novel environments vs. playing with novel objects) might modulate the degree to which infants’ posture changes the social information in view. Yet while the field has assembled many head-mounted camera datasets, conducting new analyses on these videos has remained prohibitively time-consuming due to a lack of computational tools for annotations. Instead, hundreds of hours of manual annotations have been required to analyze a fraction of the available frames for a given analysis. Thus despite containing a wealth of information about the structure of parent-child interactions, these datasets have thus gone dramatically underused.

Recent innovations in computer vision hold promise for automated annotations of the infant view. Over the past decade, deep neural networks have become dramatically better at a wide range of visual tasks, including object classification [@simonyan2014very] scene categorization [@zhou2017places], and pose detection [@zhang2016], arguably facilitating our understanding of visual perception [@peterson2018evaluating; @vanrullen2017perception] and improving computational neuroscience [@kietzmann2018deep]. However, as most models have been trained on photographs or videos taken from the adult perspective, it is still unclear how easily these models can be applied to videos taken from the infant perspective.

In the present paper, we make progress on understanding the relationship  between the infant visual perspective and motoric and linguistic development in three ways. First, we validate a model for the automated detection of faces and hands in the infant view. We use an open-source model of pose detection -- OpenPose [@zhang2016; @cao2017realtime] -- that provides pose, face, and hand keypoints for every person in an image.  We compare the detection accuracy of this method with that of both older and more specialized models of face detection, and demonstrate the usability of this off-the-shelf model for quantifying the faces and hands in the infant view.

Second, we provide an annotated, open dataset for researchers to examine the effects of postural developments and naming behavior during naturalistic parent-child interactions. To do so, we invited caregivers of 8, 12, and 16-month-olds to participate in play sessions where they were provided with pairs of novel and familiar objects (e.g., a ball and a microfiber duster, called a "zem"). We chose this age-range to span the months when infants typically transition from sitting to crawling to standing, and documented the infant egocentric view as well as a third-person view of the play session. We then annotated infants' in-the-moment posture and orientation relative to their caregiver, and obtained full transcripts of the play sessions as well as MacArthur-Bates Communicative Development Inventories for each child.

Third, we apply our automated method to this and one other openly available head-mounted camera dataset, examining the generality of the effects of motor development on the social information in view. In Study 1, we use the cross-sectional design of our dataset to directly examine the relative contributions of age vs. in-the-moment posture on infants' visual access to social information, and use the transcriptions to examine how the availability of social cues changes relative to naming events (e.g., “Yes, you like the [ball!]”). Indeed, despite positing links between the social information in view and language development, no work to date has directly examined how the availability of social information changes around naming events in naturalistic contexts. 
In Study 2, we apply this automated method to @franchak2017see, where one-year-olds wore head-mounted eye-tracking cameras during a play session and their in-the-moment posture was hand-annotated.  Unlike in Study 1, infants and caregivers roamed a large, open playroom and explored different toys placed throughout. We thus analyze this second dataset with a first goal of  validating our automated method on a very different kind of video dataset, attempting to replicate their primary findings originally obtained with a head-mounted eye-tracker, and then further examine whether the proportion of hands in view also varies with infants’ posture. 
Broadly, we predicted that there would be differential access to social information based on children's postural developments: crawling infants would see fewer faces/hands because they would primarily be looking at the ground, while walking toddlers would have access to a richer visual landscape with greater access to the social information in their environment.

# Study 1
## Methods
Caregivers of 8, 12, and 16-month-olds were invited to participate in play sessions where they were provided with pairs of novel and familiar objects (e.g., a ball and a microfiber duster, called a "zem") in a small playroom in a lab (approximately 10' x 10'). Infants wore head-mounted cameras equipped with a fish-eye lens (see Head-mounted camera); a tripod-mounted camera captured a third-person view of the play session. Using these video data, infants' posture and orientation to their caregiver were hand-coded and annotated for the entirety of the play session. All videos were transcribed, and MacArthur CDIs were collected for all children who participated. All materials have been made publicly available on Databrary for whom the parents provided sharing consent (29/36 dyads) via [BLINDED].

### Participants
```{r echo=FALSE, include=FALSE, demographics}
all_subs <- read.csv(paste0(here::here(),"/data/demographics/all_participants.csv")) %>%
  rename(subid = subID)
inc_subs <- read.csv(paste0(here::here(),"/data/demographics/demographics_updated.csv"))
all_subs$inc <- all_subs$reason=="included"

@@

sub_summary <- all_subs %>%
  left_join(inc_subs) %>%
  group_by(age_group) %>%
  summarise(n = sum(inc),
            percent_included = mean(inc),
            age = mean(age.at.test, na.rm=TRUE),
            video_length = mean(len.min, na.rm=TRUE),
            female = sum(gender=="female", na.rm=TRUE))

colnames(sub_summary) <- c('Group','N','% incl.','Avg. age', 'Avg video length', 'Num female')

@@

To obtain this final sample, we tested `r length(all_subs$reason)` children, excluding `r sum(all_subs$reason!="included")` children for the following reasons:
`r sum(all_subs$reason=="HC technical error")` for technical issues related to the headcam (e.g., failure to record, ran out of battery),
`r sum(all_subs$reason=="would not wear camera")` for failing to wear the headcam,
`r sum(all_subs$reason=="less than 4 min HC footage")` for fewer than 4 minutes of headcam footage,
`r sum(all_subs$reason=="multiple people")` for having multiple adults present,
`r sum(all_subs$reason=="no CDI")` for missing Communicative Development Inventory (CDI) data,
`r sum(all_subs$reason=="no DV cam footage")` for missing scene camera footage,
`r sum(all_subs$reason=="infant crying")` for fussiness, and 1 for sample symmetry. 16-month-olds tolerated the head-mounted camera less well than younger infants, leading to a higher exclusion rate. All inclusion decisions were made independent of the results of subsequent analyses.

@@

We used a head-mounted camera ("headcam") that was constructed from a small camera attached to a soft elastic headband.[^2]  Initial participants wore an MD-80 camera, which was then replaced by a Veho pro camera which had better battery life and a larger view angle. The view angle of the MD-80 camera was $32^{\circ}$ horizontal by $24^{\circ}$ vertical, and we attached a fish-eye lens to the camera to increase the view angle to $64^{\circ}$ horizontal by $46^{\circ}$ vertical. The view angle of the Veho pro camera was wider, $47^{\circ}$ horizontal by $36^{\circ}$ vertical. Videos captured by MD-80/Veho cameras  were 640x480/720x480 pixels, respectively, and both cameras had a frame rate of ~30 frames per second. To ensure that detections across these different cameras were comparable, we excluded detections from the outer edges of the videos taken with the MD-80 cameras based on these view angle differences in our main analyses (i.e. excluding top/bottom 13% of the frames, and left/right 10% of the frames).

@@

However, the vertical field of view of the cameras were still considerably reduced compared to the infants' field of view, which spans around 100--120$^{\circ}$ in the vertical dimension by 6-7 months of age [@mayer1988;@cummings1988]. As we were primarily interested in the presence of faces in the child's field of view, we chose to orient the camera upwards to capture the entirety of the child's upper visual field where the child is likely to see adult faces, understanding that this decision limited our ability to detect hands (especially those of the child, which are typically found at the bottom of the visual field). We note that these limitations regarding field of view and camera angle affect all studies using this method, not only our own.

@@

#### Posture and caregiver orientation annotations
We created custom annotations to describe the child's physical posture (i.e. standing) and the orientation of the caregiver relative to the child (e.g. far away). The child's posture was categorized as being carried, prone (crawling or lying), sitting, or standing. The caregiver's orientation was characterized as being close, far, or behind the child (independent of distance). For the first two annotations (close/far from the child), the caregiver could either be to the front or side of the child. All annotations were made by a trained coder using the OpenSHAPA/Datavyu software [@adolph2012toward]. Times when the child was out of view of the tripod camera were marked as uncodable and were excluded from these annotations; similarily, times when the child was being carried or the caregivers were out of the frame were marked as uncodable for caregiver orientation. On average, posture or orientation was uncodable from 1-2 minutes of data in each child (seconds excluded from analysis for posture, M = `r round(NA_rates$mean_na_posture,0)`s, SD = `r round(NA_rates$sd_na_posture,0)`s; orientation; M = `r round(NA_rates$mean_na_posture,0)`s, SD = `r round(NA_rates$sd_na_posture,0)`s), and these rates did not vary substantially with the age of the child.  To assess the reliability of these annotations, a second coder annotated videos from three different children to calculate Cohen's kappa (posture, $\kappa$ = .82; caregiver orientation, $\kappa$ = .73).

#### Naming event annotations 
One coder listened to all of the audio from the play sessions and marked the exact timestamps whenever one of the novel or familiar objects was named in any instance (e.g., "Look at the [ball]", "Can you say [zem]?"); a second coder listened to the majority of the play sessions (N = 23 sessions) and also annotated all naming events. To asesess reliability, we calculated the proportion of naming events detected by the first coder that were also annotated by the second coder within a sliding window. We found that 82.1% of naming events were detected within a 4 second window (+/- 2s), and 70.9% of namings events were detected within a 2 second window (+/- 1s). We also obtained full text transcriptions of the entire play sessions (with time stamps marking 10s intervals). While these full transcriptions are not used in the present analyses, they have been made publically avaliable for future research.

@@

## Results
First, we report the accuracy of the automated detectors, as assessed by comparison to hand-labelled frames from the free-play video dataset described above. We then apply one of these automated detectors (OpenPose) to the entirety of this video dataset, and use these outputs to examine how postural developments influence children's visual access to faces and hands from 8-16 months of age. We further use the detections to examine how access to these social cues changes during naming events (e.g., do you see the [zem]?).

@@

perfWristsOverall<- performanceWrists %>%
  group_by(detectorType) %>%
  summarise(tp=sum(result == "TP"), fp=sum(result == "FP"), fn=sum(result=="FN")) %>%
  group_by(detectorType) %>%
  summarise(p = tp / (tp + fp), r = tp / (tp + fn), f=( 2 * p * r )/ (p + r))

@@

```{r calcPostAndOrient}
## Calculate distributions of infants spent in each category separately for posture / orientation
ages_inc_subs <- inc_subs %>%
  select(age.at.test, age.grp, subid)

orientation <- d %>%
  filter(!is.na(orientation)) %>%
  group_by(age.grp, subid, orientation) %>%
  summarise(time = sum(dt, na.rm=TRUE)) %>%
  mutate(prop.time = time/sum(time)) %>%
  group_by(subid, age.grp, orientation) %>%
  left_join(ages_inc_subs)

posture <- d %>%
  filter(!is.na(posture)) %>%
  group_by(age.grp, subid, posture) %>%
  summarise(time = sum(dt, na.rm=TRUE)) %>%
  mutate(prop.time = time/sum(time)) %>%
  group_by(subid, age.grp, posture) %>%
  left_join(ages_inc_subs)
```

@@

posture_labels = c(
  carry = 'Infant carried',
  prone = 'Infant prone',
  sit = 'Infant sitting',
  stand ='Infant standing'
)

>>>>

  How do postural developments affect infants’ access to social information? We recorded egocentric and third-person video while infants and their caregivers (N=36, 8–16-month-olds) participated in naturalistic play sessions. We then validated the use of a neural network pose detection model to detect faces and hands in the infant view. We used this automated method to analyze our data and a prior egocentric video dataset (N=17, 12-month-olds). Infants’ average posture and orientation with respect to their caregiver changed dramatically across this age range; both posture and orientation modulated access to social information. Together, these results confirm that infant’s ability to move and act on the world plays a significant role in shaping the social information in their view.

keywords          : "Postural developments, headcam, social information, face detection, pose detection"
wordcount         : "8148"

@@

figsintext        : no
figurelist        : yes
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

@@

```{r, libraries include=FALSE}
library(knitr)
knitr::opts_chunk$set(fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=FALSE, message = FALSE, sanitize = TRUE)

library(here)
library(readr)
library(dplyr)
library(tidyr)
library(xtable)
library(lubridate)
library(langcog)
library(ggplot2)
library(ggthemes)
library(lme4)
library(gridExtra)
library(assertthat)
library(tidyverse)
library(viridis)
library(papaja)
library(png)
library(magick)
library(lmerTest)
```

@@

From their earliest months, infants are deeply engaged in learning from others. Even newborns tend to prefer to look at faces with direct vs. averted gaze [@farroni2002eye] and young infants follow overt gaze shifts [@gredeback2010development; @bruner1975]. And as infants reach their first birthday, they also tend to follow [@yu2013joint; @yu2017hand] and imitate the gestures of their caregivers (e.g., pointing). Infants' ability to process these social cues may provide strong scaffolding for early word learning. Longitudinal studies provide some evidence for this link: children’s level of joint engagement with their mother at 9-12 months predicts both their receptive and productive vocabularies [@carpenter1998] and 10 month-olds who follow an adult’s gaze (in an experimental context) have larger vocabularies at 18 months and throughout the second year of life [@brooks2005; @brooks2008]. While the relationship between hand-following and language development has been less well characterized, infants who follow their caregivers’ hands tend to be those who spend more time jointly attending to events with their caregivers [@yu2017hand] and caregivers tend to create referential clarity by holding objects for their infants to see [@suanda2019signal].

Relatively little work, however, has quantified how often infants see and use these kinds of social cues in naturalistic learning environments. By using head-mounted cameras to record what infants see, researchers have begun to document the infant egocentric perspective [@yoshida2008] and to quantify the information -- social and otherwise -- available to infants as they learn. While head-mounted camera data do not provide explicit information about what infants are looking at (unlike head-mounted eye-trackers), some work suggests that infants orient their head towards what they are focusing on -- putting those people or objects in view [@yoshida2008]. Initial recordings using this technique during in-lab play sessions revealed a different view than many imagined: instead of being dominated by faces, the infant perspective contained close up views of primarily toys and hands [@yoshida2008; @franchak2011; @yu2017hand]. Subsequent research has revealed that the infant view undergoes dramatic changes as infants grow. Recordings from home environments suggest that the viewpoints of very young infants -- less than 4 months of age -- do indeed contain persistent and frequent views of faces [@fausey2016; @jayaraman2017faces] but that the infant view tends to contain more and more hands as infants grow older.

Broadly, the field is in need of computational tools to reuse these rich video datasets and understand the generalizability of findings across populations, tasks, and age-ranges and to understand how changes in the infant view are influenced by other aspects of development. For example, children’s evolving motoric abilities likely change how they participate with their caregivers in different kinds of play sessions (e.g., exploring novel environments vs. playing with novel objects) which in turn may shape the social cues that children see and use during learning. Yet while the field has assembled many head-mounted camera datasets, conducting new analyses on these videos has remained prohibitively time-consuming due to a lack of computational tools for annotations. Instead, hundreds of hours of manual annotations have been required to analyze a fraction of the available frames for a given analysis. Thus, despite containing a wealth of information about the structure of parent-child interactions, these datasets have thus gone dramatically underused. As a result, an understanding of the nuanced relationship between the social information in the infant view and children’s motoric and linguistic development has remained challenging.

Indeed, developmental changes in the infant view are likely the downstream consequence of myriad factors, including infants’ evolving locomotive abilities: an infant’s ability to sit, crawl, stand, or walk structures the way they interact with the things and people in their world. These motoric developments have been thought of as gateways that open up entirely new phases of development [@iverson2010] causing a cascade of changes in an infant’s ability to interact with their world and the people in it [@karasik2014].

Thus, one idea is that infants’ changing locomotor abilities could shape the social cues that infants see and seek out, in turn impacting their cognitive and linguistic abilities. Some evidence supports this view: for example, infants’ experience with sitting predicts their success at 3D object completion tasks [@soska2010systems] as well as their receptive vocabulary [@libertus2016sit], suggesting the importance of focused play sessions for language development.  Later, as children begin crawling [@adolph1998learning] – or scooting or cruising [@patrick2012developmental] – their view of the world changes as they are no longer constrained to the same spot that their caregivers last placed them in. Yet while crawlers can choose where to go and what they see to a much greater degree, they also appear to spend much of their time in a world populated by floors and knees; during spontaneous play, toddlers are more likely to look at the floor while crawling than while walking [@franchak2011],, when they have full visual access to their environment and the people in it [@kretch2014].

On one theoretical view, it is primarily children’s ability to stand and walk that fundamentally changes their ability to access social information (e.g., facial expressions, gaze cues, pointing) relative to children who are still crawling and sitting, which could in turn allow infants to learn words quicker and more efficiently [@walle2016infant]. Supporting this idea, walking vs. crawling infants tend to make different kinds of object-related bids for attention from their caregivers [@karasik2014], hear more action directed statements (e.g., “open it”) [@karasik2014], and have higher receptive and productive vocabularies [@walle2014]. However, not all evidence supports this view: parental report data suggest no relationship between walking and the onset of language [@moore2019point]. Further, using head-mounted eye-tracking data from one-year-olds, Franchak et al., 2018 found that infants’ in-the-moment posture also interacts with their caregivers’ posture to shape the social information in view [@franchak2018see], highlighting the need to consider not only children’s motoric abilities but how caregivers adapt to them.

Recent innovations in computer vision hold promise for understanding the generality of these findings. By automating annotations of the infant view, we can go beyond limited sets of manual annotations to characterize the consistency and variability in the social information that children see during early learning. Over the past decade, deep neural networks have become dramatically better at a wide range of visual tasks, including object classification [@simonyan2014very] scene categorization [@zhou2017places], and pose detection [@zhang2016], arguably facilitating our understanding of visual perception [@peterson2018evaluating; @vanrullen2017perception] and improving computational neuroscience [@kietzmann2018deep]. Yet as most models have been trained on photographs or videos taken from the adult perspective, it is unclear how easily these models can be applied to videos taken from the infant perspective. While some computer vision algorithms have indeed been adapted for egocentric vision (e.g., gaze predictions, [@zhang2018coarse]), very few have been adapted for egocentric video data from infants [@bambach2015lending].

Here, we make progress on understanding the social information in the changing infant view by adapting novel computational methods. We use a publicly available pose detection model [@cao2017realtime; @zhang2016]) for the detection of faces and hands in infant egocentric video data, a similar approach to that used by @long2020detecting.  We compare the detection accuracy of this method with that of both older and more specialized models of face detection, demonstrating the usability of this off-the-shelf model for quantifying the faces and hands in the infant view in egocentric video datasets.

We then use these automated detections to examine how the social information in view changes with respect to infant’s age and real-time posture in two different egocentric video datasets.  In Study 1, we use the cross-sectional design of our dataset to examine the relative contributions of children’s age vs. real-time posture on infants’ visual access to social information, and use the transcriptions to explore how the availability of social cues changes relative to naming events (e.g., “Yes, you like the [ball!]”).  Indeed, despite positing links between the social information in view and language development, no work to date has directly examined how the availability of social information changes around naming events in naturalistic contexts. In Study 2, we apply this same automated method to @franchak2018see, where one-year-olds wore head-mounted eye-tracking cameras during a play session and their in-the-moment posture was hand-annotated (https://nyu.databrary.org/volume/135). Unlike in Study 1, infants and caregivers roamed a large, open playroom and explored different toys placed throughout. We analyze this second dataset with the goal of validating our automated method on a very different kind of video dataset, extending their primary findings originally obtained with a head-mounted eye-tracker. Across both datasets, we predicted that there would be differential access to social information based on children’s postural developments in both datasets: crawling infants would see fewer faces/hands because they would primarily be looking at the ground, while walking toddlers would have access to a richer visual landscape with greater access to the social information in their environment.

To preview our results, we find that infants’ changing locomotor abilities are a major factor that shape the statistics of the social visual environment, confirming and extending previous work. Thus, children’s social learning environments appears to change dramatically as children change in their ability to move on their own and interact with the world, in line with recent proposals emphasizing the child as an active learner [@xu2019towards]

# Study 1
## Methods
We provide an annotated, open dataset for researchers to examine the effects of postural developments and naming behavior during naturalistic parent-child interactions.  Caregivers of 8, 12, and 16-month-olds were invited to participate in play sessions where they were provided with pairs of novel and familiar objects (e.g., a ball and a microfiber duster, called a “zem”) in a small playroom in a lab (approximately 10 x 10 feet). Infants wore head-mounted cameras (see Head-mounted camera) and a tripod-mounted camera captured a third-person view of the play session. Using these video data, infants’ posture and orientation to their caregiver were hand-coded and annotated for the entirety of the play session; this age-range spans the months when infants typically transition from sitting to crawling to standing All videos were transcribed, and MacArthur CDIs were collected for all children who participated. All materials have been made publicly available on Databrary for whom the parents provided sharing consent (29/36 dyads) via [BLINDED].

### Participants
```{r echo=FALSE, include=FALSE, demographics}
all_subs <- read.csv(paste0(here::here(),"/data/demographics/all_participants.csv")) %>%
  rename(subid = subID)

inc_subs <- read.csv(paste0(here::here(),"/data/demographics/demographics_updated.csv")) %>%
  mutate(camera = factor(Fisheye, levels = c('no','yes'), labels = c('veho','md80')))

all_subs$inc <- all_subs$reason=="included"

@@

sub_summary <- all_subs %>%
  left_join(inc_subs) %>%
  group_by(age_group) %>%
  summarise(n = sum(inc),
            percent_included = mean(inc),
            age = mean(age.at.test, na.rm=TRUE),
            age_min = min(age.at.test, na.rm=TRUE),
            age_max = max(age.at.test, na.rm=TRUE),
            video_length = mean(len.min, na.rm=TRUE),
            female = sum(gender=="female", na.rm=TRUE))

colnames(sub_summary) <- c('Group','N','% incl.','Avg. age', 'Min age','Max age','Avg video length', 'Num female')

ages_inc_subs <- inc_subs %>%
  select(subid, age.at.test, age.grp, camera)

@@

To obtain this final sample, we tested `r length(all_subs$reason)` children, excluding `r sum(all_subs$reason!="included")` children for the following reasons:
`r sum(all_subs$reason=="HC technical error")` for technical issues related to the headcam (e.g., failure to record, ran out of battery),
`r sum(all_subs$reason=="would not wear camera")` for failing to wear the headcam,
`r sum(all_subs$reason=="less than 4 min HC footage")` for fewer than 4 minutes of headcam footage,
`r sum(all_subs$reason=="multiple people")` for having multiple adults present,
`r sum(all_subs$reason=="no CDI")` for missing Communicative Development Inventory (CDI) data,
`r sum(all_subs$reason=="no DV cam footage")` for missing scene camera footage,
`r sum(all_subs$reason=="infant crying")` for fussiness, and 1 for sample symmetry. Technical issues related to the initial headcam model (MD-80) led us to switch to a different head-mounted camera during data collection (see Head-mounted camera). 16-month-olds tolerated the head-mounted camera less well than younger infants, leading to a higher exclusion rate. All inclusion decisions were made independent of the results of subsequent analyses.

@@

We used a head-mounted camera ("headcam") that was constructed from a small camera attached to a soft elastic headband.[^2]  Initial participants wore an MD-80 camera, which was then replaced by a Veho pro camera which had better battery life and a larger view angle. The view angle of the MD-80 camera was $32^{\circ}$ horizontal by $24^{\circ}$ vertical, and we attached a fish-eye lens to the camera to increase the view angle to $64^{\circ}$ horizontal by $46^{\circ}$ vertical. The view angle of the Veho pro camera was wider, $47^{\circ}$ horizontal by $36^{\circ}$ vertical. Videos captured by MD-80/Veho cameras  were 640x480/720x480 pixels, respectively, and both cameras had a frame rate of ~30 frames per second. To ensure that detections across these different cameras were comparable, we excluded detections from the outer edges of the videos taken with the MD-80 cameras based on these view angle differences in our main analyses (i.e. excluding top/bottom 13% of the frames, and left/right 10% of the frames), and the camera that was used was included as a covariate in our generalized linear mixed effect models.

@@

However, the vertical field of view of the cameras were still considerably reduced compared to the infants' field of view, which spans around 100--120$^{\circ}$ in the vertical dimension by 6-7 months of age [@mayer1988;@cummings1988]. As we were primarily interested in the presence of faces in the child's field of view, we chose to orient the camera upwards to capture the entirety of the child's upper visual field where the child is likely to see adult faces, understanding that this decision limited our ability to detect hands (especially those of the child, which are typically found at the bottom of the visual field). We note that these limitations regarding field of view and camera angle affect all studies to date using this method, not only our own; future innovations in lightweight, wearable cameras may alleviate these field-of-view limitations.

@@

#### Posture and caregiver orientation annotations
We created custom annotations to describe the child's physical posture (i.e. standing) and the orientation of the caregiver relative to the child (e.g. far away). The child's posture was categorized as being carried, prone (crawling or lying), sitting, or standing. The caregiver's orientation was characterized as being close, far, or behind the child (independent of distance). “Close” to the caregiver was defined as being within the caregiver’s reach in any direction; for the first two annotations (close/far from the child), the caregiver could either be to the front or side of the child. When children were sitting in their caregiver’s lap, this was characterized as the caregiver being “behind” with the child sitting (instead of the child being carried);coding instructions accompany the repository for this dataset.  All annotations were made by a trained coder using the OpenSHAPA/Datavyu software [@adolph2012toward]. Times when the child was out of view of the tripod camera were marked as uncodable and were excluded from these annotations; similarly, times when the child was being carried or the caregivers were out of the frame were marked as uncodable for caregiver orientation. On average, posture or orientation was uncodable from 1-2 minutes of data in each child (seconds excluded from analysis for posture, M = `r round(NA_rates$mean_na_posture,0)`s, SD = `r round(NA_rates$sd_na_posture,0)`s; orientation; M = `r round(NA_rates$mean_na_orientation,0)`s, SD = `r round(NA_rates$sd_na_orientation,0)`s), and these rates did not vary substantially with the age of the child.  To assess the reliability of these annotations, a second coder annotated videos from five different children to calculate Cohen's kappa (posture, $\kappa$ = .76; caregiver orientation, $\kappa$ = .65).

#### Naming event annotations 
One coder listened to all of the audio from the play sessions and marked the exact timestamps whenever one of the novel or familiar objects was named in any instance (e.g., "Look at the [ball]", "Can you say [zem]?"); a second coder listened to the majority of the play sessions (N = 23 sessions) and also annotated all naming events. To asesess reliability, we calculated the proportion of naming events detected by the first coder that were also annotated by the second coder within a sliding window. We found that 82.1% of naming events were detected within a 4 second window (+/- 2s), and 70.9% of namings events were detected within a 2 second window (+/- 1s). We also obtained full text transcriptions of the entire play sessions (with time stamps marking 10s intervals). While these full transcriptions are not used in the present analyses, they have been made publicly available for future research.

@@

## Results
First, we report the accuracy of the automated detectors, as assessed by comparison to hand-labelled frames from the free-play video dataset described above. We then apply one of these automated detectors (OpenPose) to the entirety of this video dataset, and use these outputs to examine how postural developments influence children's visual access to faces and hands from 8-16 months of age. We further use the detections to examine how access to these social cues changes during naming events (e.g., do you see the [zem]?). Our main analyses were not pre-registered though they were driven by the hypotheses and findings in @frank2012measuring and @franchak2018see. In contrast, we did not have strong predictions regarding how access to social cues would change during naming, thus we consider these analyses completely exploratory. All data and code for all analyses are available at https://osf.io/bje2u/?view_only=3e2bdfbe2294422a9decca74313856f3.

@@

perfWristsOverall<- performanceWrists %>%
  group_by(detectorType) %>%
  summarise(tp=sum(result == "TP"), fp=sum(result == "FP"), fn=sum(result=="FN")) %>%
  group_by(detectorType) %>%
  summarise(p = tp / (tp + fp), r = tp / (tp + fn), f=( 2 * p * r )/ (p + r)) 
```

```{r include=FALSE, eval=FALSE}
# perfWristsByCamera <- performanceWrists %>%
#   left_join(ages_inc_subs, by = c("video" = "subid")) %>%
#   group_by(detectorType, camera) %>%
#   summarise(tp=sum(result == "TP"), fp=sum(result == "FP"), fn=sum(result=="FN")) %>%
#   group_by(detectorType, camera) %>%
#   summarise(p = tp / (tp + fp), r = tp / (tp + fn), f=( 2 * p * r )/ (p + r)) 
# 
# perfFacesByCamera <- performanceFaces %>%
#   left_join(ages_inc_subs, by = c("video" = "subid")) %>%
#   group_by(detectorType, camera) %>%
#   summarise(tp=sum(result == "TP"), fp=sum(result == "FP"), fn=sum(result=="FN")) %>%
#   group_by(detectorType, camera) %>%
#   summarise(p = tp / (tp + fp), r = tp / (tp + fn), f=( 2 * p * r )/ (p + r))

@@

```{r calcPostAndOrient}
## Calculate distributions of infants spent in each category separately for posture / orientation
ages_inc_subs <- inc_subs %>%
  select(age.at.test, age.grp, subid, camera)

orientation <- d %>%
  filter(!is.na(orientation)) %>%
  group_by(age.grp, subid, orientation) %>%
  summarise(time = sum(dt, na.rm=TRUE)) %>%
  mutate(prop.time = time/sum(time), sum_time = sum(time)) %>%
  group_by(subid, age.grp, orientation) %>%
  left_join(ages_inc_subs)

posture <- d %>%
  filter(!is.na(posture)) %>%
  group_by(age.grp, subid, posture) %>%
  summarise(time = sum(dt, na.rm=TRUE)) %>%
  mutate(prop.time = time/sum(time), sum_time = sum(time)) %>%
  group_by(subid, age.grp, posture) %>%
  left_join(ages_inc_subs)
```

@@

posture_labels = c(
  carry = 'Infant carried',
  prone = 'Infant prone',
  sit = 'Infant sitting',
  stand ='Infant standing'
)
```

```{r}
